Introductory Physics Labs: A Tale of Two Transformations

### 2021-03-30 manuscript/onlineLabPaper.tex
Squashed warnings thrown by bibtex
fixed a typo before I pushed.  Probably means that there are 2 more I can't find right now.

@@

The physics labs at our institution in Fall 2016 very much mirrored the national narrative.
The lab curriculum had been largely unchanged for about 20 years. Moreover, the equipment and
techniques used by students was outdated---triple beam balances and hand-drawn graphs were
standard.  That same year, as part of an interdisciplinary team interested in engaging students
in and assessing scientific practices, we secured funding, both internally and from the NSF, to
change this \emph{status quo} in physics, biology, and chemistry.  All three departments
transformed their labs using the Argument Driven Inquiry
(ADI)\citep{Sampson2011,Walker2011,Walker2016} pedagogical framework, which has been
specifically designed to engage students in authentic science practices. ADI is very much in
the spirit of transformations such as Modeling Physics\cite{modelingBrewe2008} and the
Investigative Science Learning Environment (ISLE) \cite{etkina2007investigative}. Oftentimes,
both Modeling Physics and ISLE are implemented in studio-style or even lecture classrooms,
whereas ADI is lab-focused. The common use of hybrid courses for Modeling and ISLE imply a
shorter time scale, for example, an ISLE cycle should take place over the course of a week,
whereas the cycles that we use in ADI take place over 4 weeks. For our institutional
transformation of our physics labs with ADI, we also utilized the AAPT Lab Recommendations to
inform our curricular choices.\citep{kozminski2014aapt}

>>>>

\bibliographystyle{apsrev4-2}

@@

The physics labs at our institution in Fall 2016 very much mirrored the national narrative.
The lab curriculum had been largely unchanged for about 20 years. Moreover, the equipment and
techniques used by students was outdated---triple beam balances and hand-drawn graphs were
standard.  That same year, as part of an interdisciplinary team interested in engaging students
in and assessing scientific practices, we secured funding, both internally and from the NSF, to
change this \emph{status quo} in physics, biology, and chemistry.  All three departments
transformed their labs using the Argument Driven Inquiry
(ADI)\citep{Sampson2011,Walker2011,Walker2016} pedagogical framework, which has been
specifically designed to engage students in authentic science practices. ADI is very much in
the spirit of transformations such as Modeling Physics\cite{modelingBrewe2008} and the
Investigative Science Learning Environment (ISLE) \cite{etkina2007investigative}. Oftentimes,
both Modeling Physics and ISLE are implemented in studio-style or even lecture classrooms,
whereas ADI is lab-focused. The common use of hybrid courses for Modeling and ISLE imply a
shorter time scale for their learning cycles, for example, an ISLE cycle often takes place over
the course of a week, whereas the cycles that we use in ADI take place over 4 weeks. For our
institutional transformation of our physics labs with ADI, we also utilized the AAPT Lab
Recommendations to inform our curricular choices.\citep{kozminski2014aapt}
